The binary liquid model for gravity-driven microchannel simulations

### 2010-10-21 Text/paper.tex
Added the initialization results to the text.

After one resolves necessary parameters to run a simulation, one needs to
initialize the macroscopic fields and populations.
The velocity is initialized with $0$ everywhere. Populations are initialized
with the equilbrium values for the binary liquid model including all the phase
gradients and laplacians. The liquid phase is initialized with $1$ and the
gas phase is initialized with $-1$. Though the initialization film thickness
is not involved in the final result for the front meniscus, Fig.
\ref{fig:different:initialization:widths}, we keep the initialized film
thickness as close as possible to the already obtained numerical film
thicknesses \cite{giavedoni-numerical}. Otherwise, the region where the
Bretherton phenomena occurs is dillute, which is obviously seen for the
simulation initialized with the film thickness as $Ny-28$ {\color{red} Michal,
can you please prepare the simulations with the different initialization. Or
just delete different thicknesses initialization}.
\begin{figure}
\includegraphics*[bb=18 350 594 450,width=0.97\textwidth]
{Figures/force_width_6.eps}
\includegraphics*[bb=18 350 594 450,
width=0.97\textwidth]{Figures/force_width_10.eps}
\includegraphics*[bb=18 350 594 450,
width=0.97\textwidth]{Figures/force_width_14.eps}
\caption{\color{red} The phase plots for different bubble widths as
$Ny-12$,$Ny-20$ and
$Ny-28$. Michal, could you please prepare nice pictures for
simulations. Indicate as well the
grid and time steps\label{fig:different:initialization:widths}}
\end{figure}

>>>>

After one resolves necessary parameters to run a simulation, one needs to
initialize the macroscopic fields and populations.
The velocity is initialized with $0$ everywhere. Populations are initialized
with the equilbrium values for the binary liquid model including all the phase
gradients and laplacians. The liquid phase is initialized with $1$ and the
gas phase is initialized with $-1$. Though the initialization film thickness
is not involved in the final result for the front meniscus, Fig.
\ref{fig:different:initialization:widths}, we keep the initialized film
thickness as close as possible to the already obtained numerical film
thicknesses \cite{giavedoni-numerical}. Otherwise, the simulation time for the
bubble to obtain a steady-state form increases.
\begin{figure}
\includegraphics*[bb=-20 360 620 430,width=0.97\textwidth]
{Figures/Init/initbegin12.eps}
\includegraphics*[bb=-20 360 620 430,
width=0.97\textwidth]{Figures/Init/initbegin16.eps}
\includegraphics*[bb=-20 360 620 430,
width=0.97\textwidth]{Figures/Init/initbegin20.eps}
\includegraphics*[bb=-20 360 620
430,width=0.97\textwidth]{Figures/Init/initfinish12.eps}\\
\includegraphics*[bb=-20 360 620
430,width=0.97\textwidth]{Figures/Init/initfinish16.eps}\\
\includegraphics*[bb=-20 360 620
430,width=0.97\textwidth]{Figures/Init/initfinish20.eps}\\
\caption{The phase plots for different bubble widths as
$H_{eff}-12$,$H_{eff}-16$ and
$H_{eff}-20$. The grid for the simulation is $102\mathrm{x}1501$. The phase
profiles were obtained after $200000$ time steps. One can see that even the
system is initialized with different bubble volumes the system comes to the
shape, where the film thickness is conserved. For the given parameters the
interface thickness is $0.0615$, $0.0611$, $0.0605$.
\label{fig:different:initialization:widths}}
\end{figure}
